Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-23 paper/ms.tex
Update paper to include correct figures
Add table with orbits
Update ref to table

\subsection{Quantification} \label{ssec:quant}
First, we illustrate the time-dependence of one possible inaccurate reference
frame. We begin by taking an orbit with initial position $(8, 0, 0)\,\kpc$ and
initial velocity $(0, -190, 30)\,\kms$ --- this corresponds to an orbit with
actions $(J_r, L_z, J_z) = (37.9, -1520, 7.0)\,\actunit$ and
$z_{\text{max}}=425\,\pc$. The orbit is plotted in \Gus{Appendix x}. We then
suppose that an observer makes observations of this orbit in a coordinate
system that is incorrect in height by $100\,\pc$ --- i.e. we subtract the
vector $(0, 0, 100)\,\pc$ from each position in the orbit. This corresponds to
an observer physically located at the position $(8, 0, 0)\,\kpc$ but
erroneously thinking they are located at $(8, 0, 0.1)\,\kpc$.

@@

\begin{figure*}
\plotone{fig/one_orbit.pdf}
\caption{The artificial phase-dependence in the observed actions induced by an
error in the Galactocentric coordinate system. We consider here an orbit with
initial position $(8,0,0)\,\kpc$ and initial velocity $(0,-190,30)\,\kms$.
This corresponds to an orbit with actions $(J_r, L_z, J_z) = (37.9, -1520,
7.0)\,\actunit$ and $z_{\text{max}}=425\,\pc$. We integrate the orbit
according to the procedure laid out in Section~\ref{ssec:action_comp}. Then,
we subtract $100\,\pc$ from the $z$ value of each position in the orbit,
corresponding to an erroneous observer assuming a midplane that is off by
$100\,\pc$. We then allow our (immortal) observer to observe the orbit over
$1\,\Gyr$ and perform the same orbit integration procedure at each timestep,
and report the values of the actions. The computation of $L_z$ is pristine to
errors in $z$, with only numerical artifacts remaining. Only small errors are
induced in $J_r$, with the middle $90\%$ of values over the $\Gyr$ being
$\sim6\%$ of the true $J_r$. As expected, large errors are induced in $J_z$,
with the middle $90\%$ of values being $\sim85\%$ of the true $J_z$.}
\label{fig:one_orbit_wrong_ref}
\end{figure*}

@@

\begin{figure*}
\plotone{fig/many_orbits_schmactions.pdf}
\caption{\Gus{update figure} We report the 95\uth minus 5\uth percentile of
the error in the measured action ($\Delta J_i$) from coordinate system errors
for three orbits with low-, medium-, and high-$J_z$ values (blue, orange, and
red, respectively). The {\em left}, {\em center}, and {\em right} panels show
the result for $J_r$, $L_z$, and $J_z$, respectively. The {\em upper} panels
consider an offset in $z$ and the {\em lower} panels consider an offset in $x$
(equivalently, an offset in the Solar radius).}
\label{fig:many_orbit_wrong_ref}
\end{figure*}

>>>>

\subsection{Quantification} \label{ssec:quant}
First, we illustrate the time-dependence of one possible inaccurate reference
frame. Throughout this work we will consider three orbits typical of the
stellar thin disk, stellar thick disk, and the stellar halo. We summarize
their initial position in phase space and the actions of their integrated
orbits in Table~\ref{tab:orbits}. Each orbit is plotted in \Gus{Appendix X}.
We will refer to these orbits by their names henceforth.

We begin by considering the thick orbit. Suppose that an observer makes
observations of this orbit in a coordinate system that is incorrect in height
by $100\,\pc$ --- i.e. we subtract the vector $(0, 0, 100)\,\pc$ from each
position in the orbit. This corresponds to an observer physically located at
the position $(8, 0, 0)\,\kpc$ but erroneously thinking they are located at
$(8, 0, 0.1)\,\kpc$.

\begin{deluxetable*}{ccccccc}
\tablehead{\colhead{name} & \colhead{initial position} & \colhead{initial
velocity} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$}\\ \colhead{ } &
\colhead{$\mathrm{kpc}$} & \colhead{$\mathrm{km}/\mathrm{s}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$}}
\startdata 
thin & $(8, 0, 0)$ & $(0, -190, 10)$ & 40.3 & -1520 & 0.69 & 122 \\
thick & $(8, 0, 0)$ & $(0, -190, 30)$ & 32.5 & -1520 & 23.0 & 425 \\ 
halo & $(8, 0, 0)$ & $(0, -190, 50)$ & 32.8 & -1520 & 529.1 & 854
\enddata
\label{tab:orbits}
\end{deluxetable*}

@@

\begin{figure*}
\plotone{fig/schmactions_one_orbit.pdf}
\caption{The artificial phase-dependence in the observed actions induced by an
error in the Galactocentric coordinate system. We consider here an orbit with
initial position $(8,0,0)\,\kpc$ and initial velocity $(0,-190,30)\,\kms$.
This corresponds to an orbit with actions $(J_r, L_z, J_z) = (37.9, -1520,
7.0)\,\actunit$ and $z_{\text{max}}=425\,\pc$. We integrate the orbit
according to the procedure laid out in Section~\ref{ssec:action_comp}. Then,
we subtract $100\,\pc$ from the $z$ value of each position in the orbit,
corresponding to an erroneous observer assuming a midplane that is off by
$100\,\pc$. We then allow our (immortal) observer to observe the orbit over
$1\,\Gyr$ and perform the same orbit integration procedure at each timestep,
and report the values of the actions. The computation of $L_z$ is pristine to
errors in $z$, with only numerical artifacts remaining. Only small errors are
induced in $J_r$, with the middle $90\%$ of values over the $\Gyr$ being
$\sim6\%$ of the true $J_r$. As expected, large errors are induced in $J_z$,
with the middle $90\%$ of values being $\sim85\%$ of the true $J_z$.}
\label{fig:one_orbit_wrong_ref}
\end{figure*}

@@

\begin{figure*}
\plotone{fig/schmactions_many_orbits.pdf}
\caption{\Gus{update figure} We report the 95\uth minus 5\uth percentile of
the error in the measured action ($\Delta J_i$) from coordinate system errors
for three orbits with low-, medium-, and high-$J_z$ values (blue, orange, and
red, respectively). The {\em left}, {\em center}, and {\em right} panels show
the result for $J_r$, $L_z$, and $J_z$, respectively. The {\em upper} panels
consider an offset in $z$ and the {\em lower} panels consider an offset in $x$
(equivalently, an offset in the Solar radius).}
\label{fig:many_orbit_wrong_ref}
\end{figure*}

\begin{figure}
\plotone{fig/schmactions_Jz_hist.pdf}
\caption{Caption.}
\label{fig:Jz_hist}
\end{figure}
